A holomorphic approach to membranes and fivebranes

### 2022-07-19 fivebranes/twisted.tex
cs

The most important equation of motion of the eleven-dimensional theory involves both the fields $\mu$ and $\gamma$. 
When $\div \mu = 0$ it takes the form
\beqn\label{eqn:eom2}
\dbar \mu + \frac12 [\mu,\mu] = \del \gamma \del \gamma .
\eeqn

@@

In the works \cite{CostelloM5,CostelloM2} Costello has introduced a program to analyze holography for membranes and fivebranes in eleven dimensional supergravity, starting with an $\Omega$-deformation of the nonminimal twists defined on multi Taub--NUT spaces.
The $\Omega$-deformation of the nonminimal twist of the eleven dimensional supergravity was constructed directly from the physical theory and was argued to admit a description in terms of a holomorphic-topological gauge theory in five dimensions.

The five-dimensional theory exists on any manifold of the form
\[
  S\times Y
\]
where $Y$ is a complex surface equipped with a holomorphic symplectic structure and $S$ is a real oriented smooth one-dimensional manifold.

The fundamental field of the five-dimensional theory is a one-form. 
The space of complex-valued one-forms on $S\times Y$ decomposes into de Rham-Dolbeault forms as
\[
\oplus_{k+p+q=1}\Omega^{k}(S)\otimes \Omega^{p,q}(Y).
\]
We continue to label elements of the homogeneous pieces as $(k;p,q)$ forms. 
The fields of ghost number zero are those one-forms with $p=0$. 
We will use the notation $\alpha^{k;q}$ with $k+q=1$ for the corresponding component of the one-form.

\brian{this is just the `semi-classical' limit of what Kevin looks at?}
These fields are subject to the equations of motion
\beqn
0 = \dbar \alpha^{0;1} + \frac{1}{2}\{\alpha^{0;1}, \alpha^{0;1}\}_Y , \qquad
0 = \d \alpha^{0;1}+\dbar \alpha^{1;0}+ \{\alpha^{0;1}, \alpha^{1;0}\}_Y
\eeqn
where $\{-,-\}_{Y}$ denotes the holomorphic Poisson bracket on $Y$ and $\d$, $\dbar$ denote the de Rham and Dolbeault differentials along $S$,$Y$ respectively.

@@

There is a non-linear gauge symmetry determined by a ghost $b \in C^\infty (S\times Y)$. 
Explicitly, the corresponding infinitesimal gauge transformation is given by
\[
\alpha^{k;q}\mapsto \alpha^{k;q} + db+\dbar b + \{b, \alpha^{k;q}\}_{Y}
\]

In the BV formalism, the full space of BV fields together with equations of motion and gauge symmetries can described by a local dg Lie algebra on $S\times Y$ whose underlying sheaf of cochain complexes is
\beqn
\Omega^\bu(S) \hotimes \Omega^{0,\bu}(Y) .
\eeqn
The holomorphic poisson bracket $\{-,-\}_{Y}$ can be extended to define a Lie bracket on the entire Dolbeault complex $\Omega^{0,\bu}(Y)$.
The dg lie algebra structure is then obtained by the tensor product with the commutative dg algebra $\Omega^\bu(S)$. 
The BV pairing is given by integrating against the holomorphic volume form on $Y$.

>>>>

The most important equation of motion of the eleven-dimensional theory involves both the fields $\mu$ and $\gamma$. 
When $\div \mu = 0$ it takes the form
\beqn\label{eqn:eom2}
\dbar \mu + \frac12 [\mu,\mu] = \del \gamma \del \gamma .
\eeqn
Because of the term on the right hand side this equation is not exactly the usual Beltrami equation for deformations of complex structures.

@@

In the works \cite{CostelloM5,CostelloM2} Costello has introduced a program to analyze holography for membranes and fivebranes in the $\Omega$-deformation of the nonminimal twist defined on multi Taub--NUT spaces.
The $\Omega$-deformation of the nonminimal twist of the eleven dimensional supergravity was constructed directly from the physical theory and was argued to admit a description in terms of a holomorphic-topological gauge theory in five dimensions.

This five-dimensional theory is formally similar to a non-commutative version of Chern--Simons theory.
It exists on any manifold of the form
\[
  S\times Y
\]
where $Y$ is a complex surface equipped with a holomorphic symplectic structure and $S$ is a real oriented smooth one-dimensional manifold.
We denote the corresponding holomorphic two-form on $Y$ by $\Omega_Y$.

There are two parameters in this theory which Costello calls $\delta$ and $\ep$.
The parameter $\delta$ controls the Chern--Simons type coupling, which in this section and going forward we will simply set to be the unit. 
The parameter $\ep$ measures the non-commutativity. 
It appears through the formal deformation quantization of~$Y$ which is the associative algebra $\cO(Y)[[\ep]]$ equipped with the Moyal product $\star$.

We consider the following subalgebra of complex-valued forms on $S\times Y$:
\[
\cL_{5d} \define \oplus_{k,q}\Omega^{k}(S)\hotimes \Omega^{0,q}(Y) \subset \Omega^\bu(S \times Y) .
\]
We continue to label elements of the homogeneous pieces as $(k;q)$ forms.
We will use the notation $\alpha^{k;q}$ with $k+q=$ for the corresponding homogenous components.
Not only is $\cL_{5d}$ a dg algebra, if we adjoin formal parameter then $\cL_{5d}[[\ep]]$ is a dg Lie algebra with respect to the Moyal commutator $[-,-]_\star$.

In the BV formalism the space of fields of the five-dimensional theory is $\cL_{5d}[[\ep]] [1]$. 
The fundamental field of the five-dimensional theory is a $\C[[\ep]]$ one-form on~$S \times Y$, which is a degree $0$ element in $\cL_{5d}[[\ep]] [1]$.

We can take a gauge condition where $\alpha^{1;0}$ vanishes.
In this case the equations of motion for the one-form field simply reads
\beqn
\dbar \alpha^{0;1} + \alpha^{0;1} \star \alpha^{0;1} = 0,
\eeqn
together with the condition that $\d_S \alpha^{0;1} = 0$.
Here $\star$ denotes the holomorphic Moyal product on $Y$ and $\d$, $\dbar$ denote the de Rham and Dolbeault differentials along $S$,$Y$ respectively.

@@

Gauge symmetries are given by degree $-1$ elements in $\cL_{5d}[[\ep]][1]$ which are simply functions $\alpha^{0;0} \in C^\infty (S\times Y)[[\ep]]$. 
Explicitly, the corresponding infinitesimal gauge transformation is given in components by
\[
\alpha^{k;q}\mapsto \alpha^{k;q} + \d_S \alpha^{0;0} +\dbar \alpha^{0;0} + \{\alpha^{0;0}, \alpha^{k;q}\}_{Y}
\]

The full BV action functional describing this model is the non-commutative Chern--Simons action
\beqn
S(\alpha) = \int_{S \times Y} \left(\frac12 \alpha \d \alpha + \frac13 \alpha \star \alpha \star \alpha \right) \wedge \Omega_Y .
\eeqn
Here, $\alpha$ represents an arbitrary element of $\cL_{5d}[[\ep]]$ and $\d$ is the full de Rham differential on $S \times Y$.

%In the BV formalism, the full space of BV fields together with equations of motion and gauge symmetries can described by a local dg Lie algebra on $S\times Y$ whose underlying sheaf of cochain complexes is
%\beqn
%\Omega^\bu(S) \hotimes \Omega^{0,\bu}(Y) .
%\eeqn
%The holomorphic poisson bracket $\{-,-\}_{Y}$ can be extended to define a Lie bracket on the entire Dolbeault complex $\Omega^{0,\bu}(Y)$.
%The dg lie algebra structure is then obtained by the tensor product with the commutative dg algebra $\Omega^\bu(S)$. 
%The BV pairing is given by integrating against the holomorphic volume form on $Y$.
